### 2020-10-26 docs/source/model.tex

  \begin{tabular}{p{15mm}p{120mm}}
    $i \in \mathcal{I}$     &  aircraft.    \\
    $t \in \mathcal{T}$     &  time periods included in the planning horizon. We use $t=0$ for starting conditions and $t=T$ for the last period. \\
    $j \in \mathcal{J}$     &  missions. \\
    $s \in \mathcal{S}$     &  intervals por deviations.
  \end{tabular}

@@

  \begin{tabular}{p{15mm}p{120mm}}
    $t \in \mathcal{T}_j$        &  time periods $t \in \mathcal{T}$ when mission $j$ is active. \\
    $j \in \mathcal{J}_i$        &  missions $j \in \mathcal{J}$ where aircraft $i$ is suitable. \\
    $j \in \mathcal{J}_t$        &  missions $j \in \mathcal{J}$ that are active in period $t$. \\
    $(t, t') \in \mathcal{L}^{M}_{i}$         & $(t \in \mathcal{T}, t' \in \mathcal{T})$ such that aircraft $i$ starts a M-cycle at the beginning of period $t$ and finishes it at the end of period $t'$. \\
    $j \in \mathcal{J}_{itt'}$         & missions $j \in \mathcal{J}_i$ that start after the beginning of period $t$ and finish before the end of period $t'$.\\
    $(t, t') \in \mathcal{L}^{VS}_{i}$         & $(t \in \mathcal{T}, t' \in \mathcal{T})$ such that aircraft $i$ starts a VS-cycle at the beginning of period $t$ and finishes it at the end of period $t'$.\\
  \end{tabular}

@@

  \begin{tabular}{p{15mm}p{100mm}p{20mm}}
    $H_j$             & total flight hours required per aircraft for mission $j$. & [hours] \\
    $R_j$             & number of aircraft required per period for mission $j$. & [aircraft] \\
    $C^{max}$         & maximum number of simultaneous aircraft checks. & [aircraft] \\
    $H^{M}$         & maximum number of flight hours between two consecutive M-checks for each aircraft. & [hours] \\
    $H^{VS}$         & maximum number of flight hours between two consecutive VS-checks for each aircraft. & [hours] \\
    $H^{rem}_{itt'}$ & remaining flight hours for aircraft $i$ at the end of the M-cycle that starts in $t$ and ends in $t'$.& [hours] \\
    $C^{rem}_{t}$ & net remaining capacity during period $t$ after discounting aircraft that go in mission.& [hours] \\
    $C^{u}_{it}$ & maintenance capacity used by aircraft $i$ in period $t$. & [days] \\
  \end{tabular}

>>>>

  \begin{tabular}{p{20mm}p{120mm}}
    $i \in \mathcal{I}$     &  aircraft.    \\
    $t \in \mathcal{T}$     &  time periods included in the planning horizon. We use $t=0$ for starting conditions and $t=T$ for the last period. \\
    $j \in \mathcal{J}$     &  missions. \\
    $s \in \mathcal{S}$     &  intervals por deviations.
  \end{tabular}

@@

  \begin{tabular}{p{20mm}p{120mm}}
    $t \in \mathcal{T}_j$        &  time periods $t \in \mathcal{T}$ when mission $j$ is active. \\
    $j \in \mathcal{J}_i$        &  missions $j \in \mathcal{J}$ where aircraft $i$ is suitable. \\
    $j \in \mathcal{J}_t$        &  missions $j \in \mathcal{J}$ that are active in period $t$. \\
    $(t, t') \in \mathcal{L}^{M}_{i}$         & $(t \in \mathcal{T}, t' \in \mathcal{T})$ such that aircraft $i$ starts a M-cycle at the beginning of period $t$ and finishes it at the end of period $t'$. \\
    $j \in \mathcal{J}_{itt'}$         & missions $j \in \mathcal{J}_i$ that start after the beginning of period $t$ and finish before the end of period $t'$.\\
    $(t, t') \in \mathcal{L}^{VS}_{i}$         & $(t \in \mathcal{T}, t' \in \mathcal{T})$ such that aircraft $i$ starts a VS-cycle at the beginning of period $t$ and finishes it at the end of period $t'$.\\
  \end{tabular}

@@

  \begin{tabular}{p{20mm}p{100mm}p{20mm}}
    $H_j$             & total flight hours required per aircraft for mission $j$. & [hours] \\
    $R_j$             & number of aircraft required per period for mission $j$. & [aircraft] \\
    $C^{max}$         & maximum number of simultaneous aircraft checks. & [aircraft] \\
    $H^{M}$         & maximum number of flight hours between two consecutive M-checks for each aircraft. & [hours] \\
    $H^{VS}$         & maximum number of flight hours between two consecutive VS-checks for each aircraft. & [hours] \\
    $H^{rem}_{itt'}$ & remaining flight hours for aircraft $i$ at the end of the M-cycle that starts in $t$ and ends in $t'$.& [hours] \\
    $C^{rem}_{t}$ & net remaining capacity during period $t$ after discounting aircraft that go in mission.& [hours] \\
    $C^{u}_{it}$ & maintenance capacity used by aircraft $i$ in period $t$. & [days] \\
  \end{tabular}
